---
title: "Outcome Item Analysis Results"
author: "Jennifer Brussow"
date: "June 26, 2017"
output: pdf_document
---

```{r setup, include=FALSE}
#general options
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
options(scipen = 999)
options(stringsAsFactors = FALSE)

needed_packages <- c("mirt", "dplyr", "tidyr", "ggplot2")
load_packages <- function(x) {
  if (!(x %in% rownames(installed.packages()))) {
    install.packages(x)
  }
  suppressPackageStartupMessages(require(x, character.only = TRUE))
}
sapply(needed_packages, load_packages)

ATI_colors <- c("#000000", "#E53935", "#80D8FF", "#FF9800", "#FFD54F", "#009688", "#CDDC39")

load_cuts <- c(-Inf, 0, 0.32, 0.45, 0.55, 0.63, 0.71, Inf)

#load data here
results_folder <- "./Results_20170630/"
fname <- "Nursing Process_analysis_result_20170630.rds"
model <- readRDS(paste0(results_folder, fname))
outcome_name <- unlist(strsplit(fname, "_"))[1]

factor_items <- readRDS(paste0(results_folder, "Nursing Process_factor-items_20170630.rds"))

outcome_code_key <- read.csv("Outcome_codes.csv")

```


```{r analysis, include = FALSE}
factor_load <- summary(model)$rotF

n_factors <- ncol(factor_load)
n_items <- nrow(factor_load)

item_f_load <- vector("list", length = length(factor_items))

for(i in 1:length(item_f_load)){
  item_f_load[[i]] <- as.data.frame(factor_load[which(rownames(factor_load) %in% factor_items[[i]]),])
}

```

#Outcome Subscores: `r outcome_name`
To investigate how accurately items are assigned to outcome categories,
a series of analyses were completed to determine items' factor loadings. 

##Dataset
The dataset analyzed consisted of responses to the 2013 Comprehensive Predictor, Forms A-F, 
from test sessions that were completed between 11/15/2015 and 12/31/2015 or
04/01/2016 or 05/15/2016. All respondents were students from BSN institutions.
Pre-test items were not included. These decisions were made in order to select
a dataset that represented optimal testing conditions.

The dataset for the `r outcome_name` outcome included XXX responses to 
`r n_items` items that were tagged to the outcome. 

##Subscore plots: 

```{r plot_setup}

subscore_plots <- vector("list", n_factors)
worst_item_ids <- vector("list", n_factors)
worst_item_loads <- vector("list", n_factors)
best_item_ids <- vector("list", n_factors)
best_item_loads <- vector("list", n_factors)

for(i in 1:n_factors){
  factor_code <- colnames(factor_load)[i]
  factor_code_sub <- gsub("F", "", factor_code)
  factor_name <- unique(outcome_code_key[which(outcome_code_key$OutcomeID_map == factor_code_sub),
                                  "OutcomeDescription_map"])
  
  plot_data <- item_f_load[[i]]
  plot_data$Loading <- cut(plot_data[, factor_code], breaks = c(load_cuts))
  
  subscore_plots[[i]] <- ggplot(data = plot_data, aes_string(x = factor_code, fill = "Loading")) + 
    geom_histogram(binwidth = 0.01, alpha = 0.7) + 
    scale_x_continuous(limits = c(-1, 1), breaks = seq(-1, 1, .2),
                       labels = seq(-1, 1, .2)) + 
    theme_bw() +
    theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5)) +
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(x = "Factor Loadings", y = "Count", 
         title = paste0(outcome_name, ": ", factor_name, " - Item Loadings"),
         caption = paste0("Mean = ", round(mean(plot_data[, factor_code]), 3),
                          ", SD = ", round(sd(plot_data[, factor_code]), 3))) +
    scale_fill_manual(values = ATI_colors, 
                       labels = c("Negatively Related", "Non-Loading", "Poor", "Fair", "Good", 
                                  "Very Good", "Excellent")) 
  
  
  
  worst_item_ids[[i]] <- rownames(plot_data[which.min(plot_data[, factor_code]),])
  worst_item_loads[[i]] <- round(min(plot_data[, factor_code]), 3)
  best_item_ids[[i]] <- rownames(plot_data[which.max(plot_data[, factor_code]),])
  best_item_loads[[i]] <- round(max(plot_data[, factor_code]), 3)
}
```

```{r analysis_out, result = "asis"}
for(i in 1:length(subscore_plots)){
  cat("\n")
  cat("###Factor code: ", gsub("F", "", colnames(factor_load)[i]))
  cat("\n")
  cat("###Factor name: ", unique(outcome_code_key[which(outcome_code_key$OutcomeID_map == 
                                                          gsub("F", "", colnames(factor_load)[i])),
                                  "OutcomeDescription_map"]))  
  cat("\n")
  print(subscore_plots[[i]])
  cat("\n\n")
  cat(paste0("Worst item: ", worst_item_ids[[i]],
             ", which had a loading of ", worst_item_loads[[i]]))
  cat("\n\n")
  cat(paste0("Best item: ", best_item_ids[[i]],
             ", which had a loading of ", best_item_loads[[i]]))
  cat("\n")
}
```

