---
output: 
  pdf_document:
    keep_tex: no
---

```{r setup, include=FALSE}
#general options
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

source("K:/AscendKC/Corp/R_and_D/1-USERS/Jennifer Brussow/options.R")

needed_packages <- c("mirt", "ggplot2", "pander")
sapply(needed_packages, load_packages)

panderOptions('knitr.auto.asis', FALSE)

load_cuts <- c(-Inf, 0, 0.32, 0.45, 0.55, 0.63, 0.71, Inf)

# graph_colors <- c("#444444", "#65007A", "#BD5701", "#000570", "#006F7D", "#008735", "#438700")
graph_colors <- c("#A1A1A1", '#ffd57f','#c7e9b4','#7fcdbb','#41b6c4','#2c7fb8','#405AC6')

#TESTING: COMMENT OUT/DELETE FOR REAL RUN
model_fname <- "Nursing Process_analysis_result_20170630.rds"
factor_items_fname <- "Nursing Process_factor-items_20170630.rds"
results_folder <- "./Results_20170630/"

# #get data from master template
# model_fname <- model_fnames[i]
# factor_items_fname <- factor_items_fnames[i]
# results_folder <- results_folder

#load data here
model <- readRDS(paste0(results_folder, model_fname))
outcome_name <- unlist(strsplit(model_fname, "_"))[1]
factor_items <- readRDS(paste0(results_folder, factor_items_fname))

outcome_code_key <- read.csv("Outcome_codes.csv")
item_content <- read.xlsx("item_content_from_QBTB-db.xlsx")

item_content[which(item_content$IsCorrect == 1), "responseopt"] <- 
  paste0(item_content[which(item_content$IsCorrect == 1), "responseopt"], " (c)")

item_content <- as.data.frame(apply(item_content, 2, FUN = iconv, from = "", to = "ASCII", sub=''))

```


```{r analysis, include = FALSE}
factor_load <- summary(model)$rotF

n_factors <- ncol(factor_load)
n_items <- nrow(factor_load)

item_f_load <- vector("list", length = length(factor_items))

for(i in 1:length(item_f_load)){
  item_f_load[[i]] <- as.data.frame(factor_load[which(rownames(factor_load) %in% factor_items[[i]]),])
}

```

#Outcome Subscores: `r outcome_name`

*`r as.Date(date, "%Y%m%d")`*

&nbsp;

To investigate how accurately items are assigned to outcome categories,
a series of analyses were completed to determine items' factor loadings. 

&nbsp;

##Dataset
The dataset analyzed consisted of responses to the 2013 Comprehensive Predictor, Forms A-F, 
from test sessions that were completed between 11/15/2015 and 12/31/2015 or
04/01/2016 or 05/15/2016. 

All respondents were students from BSN institutions.
Pre-test items were not included. These decisions were made in order to select
a dataset that represented optimal testing conditions.

The dataset for the `r outcome_name` outcome included 
`r prettyNum(nrow(extract.mirt(model, "data")), big.mark = ",")` responses to 
`r n_items` items that were tagged to the outcome. 

##Factor Loadings
Factor loadings are a way of quantifying each item's relationship to the 
underlying factor it is thought to measure. In these analyses, the factors are
the categories within the `r outcome_name` outcome. In the analysis, the construct
each factor represents is inferred from the response patterns.

Larger factor loadings are better, as they indicate that the item is more strongly
related to the factor it is thought to measure. Items with small factor loadings
generally have content that is unrelated to the factor. Items with negative factor
loadings generally contain content that is inversely related to the factor.

Factor analysis is not a perfect process.
While item content is typically thought to explain factor loadings, other item 
properties such as response mode can also influence factor loadings. Additionally, 
if items are incorrectly assigned, the factor's inferred construct 
may not actually be representative of the desired construct intended by test developers.

&nbsp;

The factor loadings in the graphs below are color-coded according to their magnitude:

* < 0.00: These items are negatively related to the factor
* 0.00 - 0.32: These items are considered non-loading, or unrelated to the factor
* 0.33 - 0.45: These items' relationship to the factor is considered poor
* 0.46 - 0.55: These items' relationship to the factor is considered fair
* 0.56 - 0.63: These items' relationship to the factor is considered good
* 0.64 - 0.71: These items' relationship to the factor is considered very good
* 0.72 - 1.00: These items' relationship to the factor is considered excellent

```{r plot_setup}

worst_item_ids <- vector("list", n_factors)
worst_item_loads <- vector("list", n_factors)
best_item_ids <- vector("list", n_factors)
best_item_loads <- vector("list", n_factors)

for(i in 1:n_factors){
  factor_code <- colnames(factor_load)[i]
  factor_code_sub <- gsub("F", "", factor_code)
  factor_name <- unique(outcome_code_key[which(outcome_code_key$OutcomeID_map == factor_code_sub),
                                  "OutcomeDescription_map"])
  
  load_data <- item_f_load[[i]]
  if(n_factors == 1){
    colnames(load_data) <- factor_code
  }
  
  load_data <- load_data[order(load_data[, factor_code], na.last = NA),]
  
  worst_item_ids[[i]] <- rownames(load_data[1:10,])
  worst_item_loads[[i]] <- round(load_data[1:10, factor_code], 3)
  best_item_ids[[i]] <- rownames(load_data[(nrow(load_data)-9):nrow(load_data),])
  best_item_loads[[i]] <- round(load_data[(nrow(load_data)-9):nrow(load_data), factor_code], 3)
}

```

```{r analysis_out, results = "asis", fig.height = 6}
for(i in 1:n_factors){
  cat("\n\n")
  cat("##Factor code: ", gsub("F", "", colnames(factor_load)[i]))
  cat("\n\n")
  cat("##Factor name: ", unique(outcome_code_key[which(outcome_code_key$OutcomeID_map == 
                                                          gsub("F", "", colnames(factor_load)[i])),
                                  "OutcomeDescription_map"]))  
  cat("\n\n")

  cat(paste0("**Worst 10 items for ", unique(outcome_code_key[which(outcome_code_key$OutcomeID_map == 
                                                          gsub("F", "", colnames(factor_load)[i])),
                                                          "OutcomeDescription_map"]),
             ":** "))
  
  for(item in 1:10){
    cat(as.character(worst_item_ids[[i]][item]),
             ", which had a loading of ", sprintf("%.f3", as.numeric(worst_item_loads[[i]][item])))
    cat("\n\n")
  
    worst_item_temp <- item_content[which(item_content$QuestionID == worst_item_ids[[i]][item]),]
    
    cat(unique(worst_item_temp$stem), "\n\n")
    cat("A. ", worst_item_temp[1, "responseopt"], "\n\n")
    cat("B. ", worst_item_temp[2, "responseopt"], "\n\n")
    cat("C. ", worst_item_temp[3, "responseopt"], "\n\n")
    cat("D. ", worst_item_temp[4, "responseopt"], "\n\n")
    
    cat("\n\n\\bigskip\n\n")
  }

  cat("\n\n\\bigskip\\bigskip\\bigskip\n\n")
  
  cat(paste0("**Best 10 items for ", unique(outcome_code_key[which(outcome_code_key$OutcomeID_map == 
                                                          gsub("F", "", colnames(factor_load)[i])),
                                                          "OutcomeDescription_map"]),
             ":** "))
  
  for(item in 1:10){
    cat(as.character(best_item_ids[[i]][item]),
             ", which had a loading of ", sprintf("%.f3", as.numeric(best_item_loads[[i]][item])))
    cat("\n\n")
  
    best_item_temp <- item_content[which(item_content$QuestionID == best_item_ids[[i]][item]),]
    
    cat(unique(best_item_temp$stem), "\n\n")
    cat("A. ", best_item_temp[1, "responseopt"], "\n\n")
    cat("B. ", best_item_temp[2, "responseopt"], "\n\n")
    cat("C. ", best_item_temp[3, "responseopt"], "\n\n")
    cat("D. ", best_item_temp[4, "responseopt"], "\n\n")
    
    cat("\n\n\\bigskip\n\n")
  }
  
  cat("\n\n")
  
  cat("***")
}
```

